The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (9th edition -- distributed with CrypTool version 1.4.20)} \vspace{60pt}

### 2008-07-04 script/de/chapters/introduction.tex
Update scripts: minimal correction (1.4.10 in menutree)
1.4.20 updates

An dieser Stelle möchte ich explizit fünf Personen danken, 
die bisher in ganz besonderer Weise zu CrypTool\index{CrypTool} 
beigetragen haben.
Ohne ihre besonderen Fähigkeiten und ihr großes Engagement wäre CrypTool
nicht, was es heute ist:
\vspace{-7pt}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Hr.\ Henrik Koy
   \item Hr.\ Jörg-Cornelius Schneider
   \item Hr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Prof. Dr. Claudia Eckert und ihre Mitarbeiter (Clausius, Buntrock).
\end{list}
Auch allen hier nicht namentlich Genannten ganz herzlichen Dank für das 
(meist in der Freizeit) geleistete Engagement.
\\

@@

>>>>

An dieser Stelle möchte ich explizit folgenden Personen danken, 
die bisher in ganz besonderer Weise zu CrypTool\index{CrypTool} 
beigetragen haben.
Ohne ihre besonderen Fähigkeiten und ihr großes Engagement wäre CrypTool
nicht, was es heute ist:
\vspace{-7pt}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Hr.\ Henrik Koy
   \item Hr.\ Jörg-Cornelius Schneider
   \item Hr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Mitarbeiter von Prof.\ Claudia Eckert, Prof.\ Johannes Buchmann und Prof.\ Torben Weiß.
\end{list}
Auch allen hier nicht namentlich Genannten ganz herzlichen Dank für das 
(meist in der Freizeit) geleistete Engagement.
\\

@@

Frankfurt, Juli 2008

### 2008-07-04 script/de/chapters/menus.tex
menu update for 1.4.10
1.4.20 updates

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{
\includegraphics[scale=0.25, angle=270, viewport=200 3 2680 1276]
                {figures/cryptool-menu-de}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\caption{Komplette Übersicht über den Menü-Baum von CrypTool 1.4.10} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

>>>>

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{
\includegraphics[scale=0.25, angle=270, viewport=200 30 2680 1420]
                {figures/cryptool-menu-de}
%viewport=rand-links? rand-unten breite hoehe [bezogen auf querformat]
%}
\caption{Komplette Übersicht über den Menü-Baum von CrypTool 1.4.20} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

### 2008-07-04 script/de/chapters/numbertheory.tex
1.4.20 updates

Für die $i$-fach aufeinander folgende modulare Multiplikation einer
Zahl $a$ mit $i=1, \cdots , m-1$ ergibt sich als Produkt das neutrale
Element der Multiplikation $(1)$ nur dann, wenn $a$ und $m$
teilerfremd\index{Zahlen!teilerfremd (co-prime)} sind.

@@

Die 2. Forderung kann leicht sichergestellt werden, weil es \glqq sehr'' viele \index{Primzahl!Anzahl}
Primzahlen gibt\footnote{%
Nach dem Primzahlsatz\index{Primzahlsatz} (prime number theorem) von 
Legendre\index{Legendre, Adrien-Marie} und Gauss\index{Gauss, Carl Friedrich}
gibt es bis zur Zahl $n$ asymptotisch $n/{\rm ln}(n)$ Primzahlen. Dies bedeutet
beispielsweise: es gibt $6,5*10^{74}$ Primzahlen unterhalb von $n=2^{256}$
$(1,1*10^{77})$ und $3,2*10^{74}$ Primzahlen unterhalb von $n=2^{255}$. 
Zwischen $2^{256}$ und $2^{255}$ gibt es also allein $3,3*10^{74}$ Primzahlen
mit genau $256$ Bits. Diese hohe Zahl ist auch der Grund, warum man sie nicht
einfach alle abspeichern kann.
} 
und weil dies durch eine zentrale Stelle, die Zertifikate ausgibt,
sichergestellt werden kann.

@@

{\bf Schritt 1:}

>>>>

Für die $i$-fach aufeinander folgende modulare Multiplikation einer
Zahl $a$ mit $i=1, \cdots , m-1$ ergibt sich als Produkt das neutrale
Element der Multiplikation nur dann, wenn $a$ und $m$
teilerfremd\index{Zahlen!teilerfremd (co-prime)} sind.

@@

Die 2. Forderung kann leicht sichergestellt werden, weil es \glqq sehr'' viele \index{Primzahl!Anzahl}
Primzahlen gibt\footnote{%
Nach dem \textbf{\hyperlink{thm-pz-pi-x}{Primzahlsatz}}\index{Primzahlsatz} (Kapitel~\ref{thm-pz-pi-x}, S.~\pageref{thm-pz-pi-x}) von 
Legendre\index{Legendre, Adrien-Marie} und Gauss\index{Gauss, Carl Friedrich}
gibt es bis zur Zahl $n$ asymptotisch $n/{\rm ln}(n)$ Primzahlen. Dies bedeutet
beispielsweise: es gibt $6,5*10^{74}$ Primzahlen unterhalb von $n=2^{256}$
$(1,1*10^{77})$ und $3,2*10^{74}$ Primzahlen unterhalb von $n=2^{255}$. 
Zwischen $2^{256}$ und $2^{255}$ gibt es also allein $3,3*10^{74}$ Primzahlen
mit genau $256$ Bits. Diese hohe Zahl ist auch der Grund, warum man sie nicht
einfach alle abspeichern kann.
} 
und weil dies durch eine zentrale Stelle, die Zertifikate ausgibt,
sichergestellt werden kann.

@@

\newpage
{\bf Schritt 1:}

### 2008-07-04 script/en/chapters/introduction.tex
Update scripts: Corrections according to feedback
1.4.20 updates

% $Id$
% ............................................................................
%      V O R W O R T  und  E I N F Ü H R U N G (Zusammenspiel Skript-CT) 
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\vspace{12pt}
The first time the document was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been expanded and revised in almost
every new version of CrypTool (1.2.02, 1.3.00, 1.3.02, 1.3.03, 1.3.04, 1.4.00
and now 1.4.00).

@@

At this point I'd like to thank explicitly the following five people who
particularly contributed to CrypTool\index{CrypTool}. Without their special
talents and engagement CrypTool would not be what it is today:
\vspace{-7pt}
%\begin{itemize}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Mr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Prof. Dr. Claudia Eckert and her staff (Clausius, Buntrock).
\end{list}
%\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\

@@

>>>>

% $Id$
% ............................................................................
%      V O R W O R T  und  E I N F ‹ H R U N G (Zusammenspiel Skript-CT) 
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

\vspace{12pt}
The first time the document was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been expanded and revised in almost
every new version of CrypTool (1.2.02, 1.3.00, 1.3.02, 1.3.03, 1.3.04, 1.4.00
and now 1.4.10).

@@

At this point I'd like to thank explicitly the following people who
particularly contributed to CrypTool\index{CrypTool}. Without their special
talents and engagement CrypTool would not be what it is today:
\vspace{-7pt}
%\begin{itemize}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Mr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Staff of Prof.\ Claudia Eckert, Prof.\ Johannes Buchmann and Prof.\ Torben Weiﬂ.
\end{list}
%\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\

@@

Frankfurt (Germany), July 2008

### 2008-07-04 script/en/chapters/menus.tex
menu update for 1.4.10
1.4.20 updates

%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{  %TeX macht einen Rehmen (siehe viewport) drumherum -- gut zum Testen
%\includegraphics[scale=0.75, angle=270, viewport=14 72 835 590]
\includegraphics[scale=0.25, angle=270, viewport=200 3 2680 1276]
                {figures/cryptool-menu-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\caption{Complete overview of the menu tree of CrypTool 1.4.10} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

>>>>

%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{  %TeX macht einen Rehmen (siehe viewport) drumherum -- gut zum Testen
\includegraphics[scale=0.25, angle=270, viewport=200 30 2660 1430]
                {figures/cryptool-menu-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\caption{Complete overview of the menu tree of CrypTool 1.4.20} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

### 2008-07-04 script/en/chapters/numbertheory.tex
1.4.20 updates

The known laws apply:
\begin{itemize}
\item[\bf 1.] {\bf Associative law:}\index{Associative law} \\ 
    $((a+b) + c) {\rm ~(mod~ } m) \equiv  (a + (b+c)) {\rm ~(mod~ } m).$ \\
    $((a*b) * c) {\rm ~(mod~ } m) \equiv  (a * (b*c)) {\rm ~(mod~ } m).$
\item[\bf 2.] {\bf Commutative law:} \index{Commutative law}\\
    $(a+b) {\rm ~(mod~ } m) \equiv  (b+a) {\rm ~(mod~ } m).$ \\
     $(a*b) {\rm ~(mod~ } m) \equiv  (b*a) {\rm ~(mod~ } m).$
\end{itemize}
The associative law and commutative law apply to both addition and multiplication.
\begin{itemize}
\item[\bf 3.] {\bf Distributive law:} \index{Distributive law}\\
    $ (a * (b+c)) {\rm ~(mod~ } m) \equiv  (a*b + a*c) {\rm ~(mod~ } m).$ 
\item[\bf 4.] {\bf Reducibility:} \index{Reducibility} \\
    $(a+b) {\rm ~(mod~} m) \equiv  (a {\rm ~(mod~ } m) + b {\rm ~(mod~ } m)) {\rm ~(mod~} m).$ \\  
    $(a*b) {\rm ~(mod~} m) \equiv  (a {\rm ~(mod~ } m) * b {\rm ~(mod~ } m)) {\rm ~(mod~} m).$ \\
    When adding or multiplying the order in which order the modulo operation is performed is irrelevant.
\end{itemize}
\begin{itemize}
\item[\bf 5.] {\bf Existence of an identity (neutral element):} \index{Identity}\\
    $(a + 0) {\rm ~(mod~ } m) \equiv  (0 + a) {\rm ~(mod~ } m) \equiv  a {\rm ~(mod~ } m).$  \\
    $(a * 1) {\rm ~(mod~ } m) \equiv  (1 * a) {\rm ~(mod~ } m) \equiv  a {\rm ~(mod~ } m).$
\item[\bf 6.] {\bf Existence of an inverse element:} \\
    For all whole numbers $a$ and $m$ there exists a whole number $-a$ such that: \\
    $(a + (-a)) {\rm ~(mod~}m) \equiv  0 {\rm ~(mod~ } m)$ \quad (additive inverse).
\index{Inverse!additive}\\
    For each $a$ ($a \not\equiv 0 {\rm ~(mod~ } p$) ) where $p$ is prime there exists a whole number $a^{-1}$, 
such that: \\
    $(a * a^{-1}) {\rm ~(mod~ } p) \equiv 1 {\rm ~(mod~}p)$ \quad (multiplicative inverse). 
\index{Inverse!multiplicative}
\item[\bf 7.] \index{Closeness} {\bf Closeness}\footnote{\label{ftn-zth-closed}The property of closeness is always defined in relation to an operation in a set. See 
\hyperlink{Appendix_B}{Appendix B of this chapter}.}:   \\
     $a, b \in G  \Longrightarrow  ( a + b ) \in G.$ \\
    $a, b \in G  \Longrightarrow  ( a * b ) \in G.$
\item[\bf 8.] \index{Transitivity} {\bf Transitivity}:

@@

\begin{itemize}
\item the addition table\footnote{Comment on subtraction modulo 5: \\
$2 - 4 = -2 \equiv 3{\rm ~mod~}5.$\\
It is therefore not true modulo $5$ that $-2 = 2$ (see also \hyperlink{Appendix_C}{Appendix C of this chapter}). }
${\rm ~(mod~ } 5)$ and
\item the multiplication tables\footnote{\label{ftn-mod6}Comment on division modulo $6$:\index{Division modulo $n$}\\
Due to the special role of zero as the identity for addition, division by zero is not permitted:\\
for all $a$ it is $a*0=0,$ because $a*0=a*(0+0)=a*0+a*0.$ Obviously $0$ has no inverse regarding the
multiplication, because if there would be one, it must be $ 0= 0*0^{-1} =1.$ Also see footnote \ref{ftn-zth-divmodn}.}
for mod $5$ and mod $6$.
\end{itemize}

@@

This is not the case, however, for 
modular multiplication.
\begin{theorem}\label{thm-zth-multinv}
A natural number $a$ from the set $\{1, \cdots, m-1\}$ has one inverse if
and only if this number and the modulo $m$ are co-prime\footnote{Two whole
numbers $a$ and $b$ are co-prime\index{Number!co-prime} if and only if
${\rm gcd}(a, b) = 1$.\\
If $p$ is prime and $a$ is a random whole number that is not a multiple of
$p$, then $p$ and a are co-prime.\\
Further name to the topic co-prime (with $a_i \in \mathbb{Z}, i=1, \cdots, n$):
\begin{enumerate}
\item $a_1,a_2, \cdots, a_n$ are {\em relatively prime} \index{Relatively prime}, if $ {\rm~gcd}(a_1, \cdots , a_n) =1.$
\item An even stronger request for more than two numbers is :\\
                $a_1, \cdots , a_n$ are {\em in pairs relatively prime}, if for all $i=1, \cdots, n$ and 
$j=1, \cdots , n$ with $ i \neq j $: $ {\rm~gcd} (a_i, a_j) =1. $
\end{enumerate}
Example: $2,3,6 $ are relatively prime, because $ {\rm~gcd} (2,3,6)=1.$ 
They are not in pairs relatively prime, because $ {\rm~gcd} (2,6)=2>1.$}\index{Gcd}, in other words if $a$ and $m$ have 
no common prime factors.
\end{theorem}
Since $m=5$ is prime, the numbers $1$ to $4$ are relatively prime to $5$ and {\bf each} of these numbers has a 
multiplicative inverse in mod $5$.

@@

\vskip +5pt
{\bf Examples for calculating a modular power:}
\begin{itemize}
\item  With $2 = 1 * 2$  and  $6 = 2*3$ where $2$ and $3$ are both prime; $J(6) = 2$ because only $1$ and $5$ are 
       relatively prime to $6$, we obtain the equation $5^2 \equiv 5^{J(6)} \equiv 1 {\rm ~(mod~} 6)$,
       without having to calculate the power.
\item  With $792 = 22 * 36$  and  $23*37 = 851$ where $23$ and $37$ are both prime, it follows that
       $31^{792} \equiv 31^{J(23*37)} \equiv 31^{J(851)} \equiv 1 {\rm ~(mod~} 851)$.
\end{itemize}

@@

For the $i$-times successive modular multiplication of a number $a$ with $i=1,\cdots, m-1$ the product is the neutral element
of the multiplication (1) if and only if $a$ and $m$ are relatively prime.

@@

The following two tables show the multiplicative orders and primitive roots modulo $45$ and modulo $46$.

@@

The 2nd requirement can easily be met because there is a ``very'' large number
of prime numbers\footnote{%
According to the prime number theorem of 
Legendre\index{Legendre, Adrien-Marie} and Gauss \index{Gauss, Carl Friedrich} 
there are approximately $n/\ln(n)$ 
prime numbers\index{Prime number!number of} up to the number $n$. 
This means, for example, that there are $6.5*10^{74}$ prime numbers 
under $n=2^{256}$ ($=1.1*10^{77}$) and $3.2*10^{74}$ prime numbers 
under $n=2^{255}$. 
Between $2^{255}$ and $2^{256}$ there are therefore $3.3*10^{74}$ prime numbers with precisely $256$ bits. This large number is 
also the reason why we cannot simply save them all.} and because this can be ensured by a central office that issues certificates.

>>>>

The known laws apply:
\begin{itemize}
\item[\bf 1.] {\bf Associative law:}\index{Associative law} \\ 
    $((a+b) + c) {\rm ~(mod~ } m) \equiv  (a + (b+c)) {\rm ~(mod~ } m).$ \\
    $((a*b) * c) {\rm ~(mod~ } m) \equiv  (a * (b*c)) {\rm ~(mod~ } m).$
\item[\bf 2.] {\bf Commutative law:} \index{Commutative law}\\
    $(a+b) {\rm ~(mod~ } m) \equiv  (b+a) {\rm ~(mod~ } m).$ \\
     $(a*b) {\rm ~(mod~ } m) \equiv  (b*a) {\rm ~(mod~ } m).$
\end{itemize}
The associative law and the commutative law apply to both addition and multiplication.
\begin{itemize}
\item[\bf 3.] {\bf Distributive law:} \index{Distributive law}\\
    $ (a * (b+c)) {\rm ~(mod~ } m) \equiv  (a*b + a*c) {\rm ~(mod~ } m).$ 
\item[\bf 4.] {\bf Reducibility:} \index{Reducibility} \\
    $(a+b) {\rm ~(mod~} m) \equiv  (a {\rm ~(mod~ } m) + b {\rm ~(mod~ } m)) {\rm ~(mod~} m).$ \\  
    $(a*b) {\rm ~(mod~} m) \equiv  (a {\rm ~(mod~ } m) * b {\rm ~(mod~ } m)) {\rm ~(mod~} m).$ \\
    When adding or multiplying the order in which the modulo operation is performed does not matter.
\end{itemize}
\begin{itemize}
\item[\bf 5.] {\bf Existence of an identity (neutral element):} \index{Identity}\\
    $(a + 0) {\rm ~(mod~ } m) \equiv  (0 + a) {\rm ~(mod~ } m) \equiv  a {\rm ~(mod~ } m).$  \\
    $(a * 1) {\rm ~(mod~ } m) \equiv  (1 * a) {\rm ~(mod~ } m) \equiv  a {\rm ~(mod~ } m).$
\item[\bf 6.] {\bf Existence of an inverse element:} \\
    For all whole numbers $a$ and $m$ there exists a whole number $-a$ such that: \\
    $(a + (-a)) {\rm ~(mod~}m) \equiv  0 {\rm ~(mod~ } m)$ \quad (additive inverse).
\index{Inverse!additive}\\
    For each $a$ ($a \not\equiv 0 {\rm ~(mod~ } p$) ) where $p$ is prime there exists a whole number $a^{-1}$, 
such that: \\
    $(a * a^{-1}) {\rm ~(mod~ } p) \equiv 1 {\rm ~(mod~}p)$ \quad (multiplicative inverse). 
\index{Inverse!multiplicative}
\item[\bf 7.] \index{Closeness} {\bf Closeness}\footnote{\label{ftn-zth-closed}The property of closeness is always defined in relation to an operation in a set. See 
\hyperlink{Appendix_B}{Appendix B of this chapter}.}:   \\
     $a, b \in G  \Longrightarrow  ( a + b ) \in G.$ \\
    $a, b \in G  \Longrightarrow  ( a * b ) \in G.$
\item[\bf 8.] \index{Transitivity} {\bf Transitivity}:

@@

\begin{itemize}
\item the addition table\footnote{Comment on subtraction modulo 5: \\
$2 - 4 = -2 \equiv 3{\rm ~mod~}5.$\\
It is therefore not true modulo $5$ that $-2 = 2$ (see also \hyperlink{Appendix_C}{Appendix C of this chapter}). }
${\rm ~(mod~ } 5)$ and
\item the multiplication tables\footnote{\label{ftn-mod6}Comment on division modulo $6$:\index{Division modulo $n$}\\
Due to the special role of zero as the identity for addition, division by zero is not permitted:\\
For all $a$ it is $a*0=0,$ because $a*0=a*(0+0)=a*0+a*0.$ Obviously $0$ has no inverse regarding the
multiplication, because if there would be one, it must be $ 0= 0*0^{-1} =1.$ Also see footnote \ref{ftn-zth-divmodn}.}
for mod $5$ and mod $6$.
\end{itemize}

@@

This is not the case, however, for 
modular multiplication.
\begin{theorem}\label{thm-zth-multinv}
A natural number $a$ from the set $\{1, \cdots, m-1\}$ has one inverse if
and only if this number and the modulo $m$ are co-prime\footnote{Two whole
numbers $a$ and $b$ are co-prime\index{Number!co-prime} if and only if
${\rm gcd}(a, b) = 1$.\\
If $p$ is prime and $a$ is a random whole number that is not a multiple of
$p$, then $p$ and a are co-prime.\\
Further name to the topic co-prime (with $a_i \in \mathbb{Z}, i=1, \cdots, n$):
\begin{enumerate}
\item $a_1,a_2, \cdots, a_n$ are {\em relatively prime} \index{Relatively prime}, if $ \mbox{gcd}(a_1, \cdots , a_n) =1.$
\item An even stronger request for more than two numbers is :\\
                $a_1, \cdots , a_n$ are {\em in pairs relatively prime}, if for all $i=1, \cdots, n$ and 
$j=1, \cdots , n$ with $ i \neq j $: $ \mbox{gcd} (a_i, a_j) =1. $
\end{enumerate}
Example: $2,3,6 $ are relatively prime, because $ \mbox{gcd} (2,3,6)=1.$ 
They are not in pairs relatively prime, because $ \mbox{gcd} (2,6)=2>1.$}\index{Gcd}, in other words if $a$ and $m$ have 
no common prime factors.
\end{theorem}
Since $m=5$ is prime, the numbers $1$ to $4$ are relatively prime to $5$ and {\bf each} of these numbers has a 
multiplicative inverse in mod $5$.

@@

\vskip +5pt
{\bf Examples for calculating a modular power:}
\begin{itemize}
\item  With $2 = 1 * 2$  and  $6 = 2*3$ where $2$ and $3$ are both prime; $J(6) = 2$ because only $1$ and $5$ are 
       relatively prime to $6$, we obtain the equation $5^2 \equiv 5^{J(6)} \equiv 1 {\rm ~(mod~} 6)$,
       without having to calculate the power.
\item  With $792 = 22 * 36$  and  $23*37 = 851$ where $23$ and $37$ are both prime, it follows for $31 \in \mathbb{Z}_{851}^*$ that
       $31^{792} \equiv 31^{J(23*37)} \equiv 31^{J(851)} \equiv 1 {\rm ~(mod~} 851)$.
\end{itemize}

@@

For the $i$-times successive modular multiplication of a number $a$ with $i=1,\cdots, m-1$ the product is the neutral element
of the multiplication if and only if $a$ and $m$ are relatively prime.

@@

\newpage
The following two tables show the multiplicative orders and primitive roots modulo $45$ and modulo $46$.

@@

The 2nd requirement can easily be met because there is a ``very'' large number
of prime numbers\footnote{%
According to the \textbf{\hyperlink{thm-pz-pi-x}{prime number theorem}} (chapter~\ref{thm-pz-pi-x}, p.~\pageref{thm-pz-pi-x}) of 
Legendre\index{Legendre, Adrien-Marie} and Gauss \index{Gauss, Carl Friedrich} 
there are approximately $n/\ln(n)$ 
prime numbers\index{Prime number!number of} up to the number $n$. 
This means, for example, that there are $6.5*10^{74}$ prime numbers 
under $n=2^{256}$ ($=1.1*10^{77}$) and $3.2*10^{74}$ prime numbers 
under $n=2^{255}$. 
Between $2^{255}$ and $2^{256}$ there are therefore $3.3*10^{74}$ prime numbers with precisely $256$ bits. This large number is 
also the reason why we cannot simply save them all.} and because this can be ensured by a central office that issues certificates.
